---
title: "How to use the ohsome API with R"
author: "Lukas Loos"
date: "5 März 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
There are different packages available to use for http requests with R. This tutorial will cover the packages **httr** and **rapiclient**.

## Prerequisites

  * install packages: httr, jsonlite, rapiclient and readtext 


---

###rapiclient###
  * https://cran.r-project.org/web/packages/rapiclient/index.html
  * https://github.com/bergant/rapiclient
  * generates functions for the API endpoints
  * no support for POST requests
  
```{r}
library(rapiclient)

api <- get_api(url= "https://api.ohsome.org/v0.9-ignite/docs?group=dataAggregation")

operations <- get_operations(api)

schemas <- get_schemas(api)

result <- operations$elementsCount(bboxes = '85.31015,27.71919,85.31828,27.72459', keys = 'building', values = 'yes', time = '2014-01-01/2017-01-01/P1Y', types = 'way')

content <- httr::content(result)

content$result[[1]]

```
---
###httr###
  * https://cran.r-project.org/web/packages/httr/index.html
  * https://cran.r-project.org/web/packages/httr/vignettes/quickstart.html
  * use httr if you want to send POST requests.


```{r}
library(httr)
library(readtext)
```

```{r}

elementsCountGroupByBoundary <- function(x) {
  
  osmKeys <- "building"
  osmTime <- "2015-03-01/2015-12-01/P1M"
  osmTypes <- "way"
  osmValues <- "yes"

    r <- POST("https://api.ohsome.org/v0.9-ignite/elements/count/groupBy/boundary", 
            encode = "form", 
            body = list(
              bpolys = x, 
              keys = osmKeys, 
              time = osmTime, 
              types = osmTypes,
              values = osmValues)
  )  
  return(r)
}
```

####POST requst using "|" delimited format####
```{r warning=FALSE}
bpolysLine <- readLines("data/example-data.lineformat")
response <- elementsCountGroupByBoundary(bpolysLine)
response$status_code
response
contentLine <- httr::content(response)
contentLine$groupByResult[[1]]$result[[1]]
```



####POST requst using geoJSON format####
```{r warning=FALSE}

geoJSON <- readtext("data/example-data.geojson")
response <- elementsCountGroupByBoundary(geoJSON$text)
response
content <- httr::content(response)
content$groupByResult[[1]]$result[[1]]
```
### request with CSV response###
```{r warning=FALSE}
elementsCountGroupByBoundaryCSV <- function(x) {
  
  osmKeys <- "building"
  osmTime <- "2015-03-01/2015-12-01/P1M"
  osmTypes <- "way"
  osmValues <- "yes"

    r <- POST("https://api.ohsome.org/v0.9-ignite/elements/count/groupBy/boundary", 
            encode = "form", 
            body = list(
              format = "csv",
              bpolys = x, 
              keys = osmKeys, 
              time = osmTime, 
              types = osmTypes,
              values = osmValues)
  )  
  return(r)
}

geoJSON <- readtext("data/example-data.geojson")
response <- elementsCountGroupByBoundaryCSV(geoJSON$text)
response 
```





