---
title: "How to use the ohsome API with R"
author: "Lukas Loos"
date: "5 März 2019"
output: rmarkdown::github_document
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile),'/README.md')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
There are different packages available to use for http requests with R. This tutorial will cover the packages **httr** and **rapiclient**.

## Prerequisites

  * install packages: httr, jsonlite, rapiclient and readtext 


---

###rapiclient###
  * https://cran.r-project.org/web/packages/rapiclient/index.html
  * https://github.com/bergant/rapiclient
  * generates functions for the API endpoints
  * no support for POST requests
  
```{r}
library(rapiclient)

api <- get_api(url= "https://api.ohsome.org/v1/docs?group=Data%20Aggregation")

operations <- get_operations(api)

schemas <- get_schemas(api)

result <- operations$elementsCount(bboxes = '85.31015,27.71919,85.31828,27.72459', filter = 'building=yes and type:polygon', time = '2014-01-01/2017-01-01/P1Y')

content <- httr::content(result)

content$result[[1]]

```
---
###httr###
  * https://cran.r-project.org/web/packages/httr/index.html
  * https://cran.r-project.org/web/packages/httr/vignettes/quickstart.html
  * use httr if you want to send POST requests.


```{r}
library(httr)
library(readtext)
```

```{r}

elementsCountGroupByBoundary <- function(x) {
  
  osmTime <- "2015-03-01/2015-12-01/P1M"

    r <- POST("https://api.ohsome.org/v1/elements/count/groupBy/boundary",
            encode = "form",
            body = list(
              bpolys = x,
              filter = 'building=yes and geometry:polygon',
              time = osmTime)
  )  
  return(r)
}
```

####POST requst using "|" delimited format####
```{r warning=FALSE}
bpolysLine <- readLines("data/example-data.lineformat")
response <- elementsCountGroupByBoundary(bpolysLine)
response$status_code
response
contentLine <- httr::content(response)
contentLine$groupByResult[[1]]$result[[1]]
```



####POST requst using geoJSON format####
```{r warning=FALSE}

geoJSON <- readtext("data/example-data.geojson")
response <- elementsCountGroupByBoundary(geoJSON$text)
response
content <- httr::content(response)
content$groupByResult[[1]]$result[[1]]
```
### request with CSV response###
```{r warning=FALSE}
elementsCountGroupByBoundaryCSV <- function(x) {
  
  osmTime <- "2015-03-01/2015-12-01/P1M"

    r <- POST("https://api.ohsome.org/v1/elements/count/groupBy/boundary",
            encode = "form",
            body = list(
              format = "csv",
              bpolys = x,
              filter = 'building=yes and geometry:polygon'
              time = osmTime)
  )  
  return(r)
}

geoJSON <- readtext("data/example-data.geojson")
response <- elementsCountGroupByBoundaryCSV(geoJSON$text)
response 
```





